### 2022-01-05 paper/paper.tex
comment on parallelization
change caption of mesh plot to indicate that it is a slice

@@

Figure~\ref{fig:jet} demonstrates sub-cell entropy-dissipative shock-capturing
methods with sub-cell positivity-preserving limiters and adaptive mesh refinement applied
to an astrophysical supersonic jet with Mach number 2000 \cite{liu2021oscillation}.
\begin{figure}[!h]
  \begin{subfigure}{0.53\linewidth}
    \includegraphics[width=\textwidth]{../figures/jet_density}
    \caption{Density at time $t = 10^{-3}$.}
  \end{subfigure}%
  \hspace*{\fill}
  \begin{subfigure}{0.47\linewidth}
    \includegraphics[width=\textwidth]{../figures/jet_mesh}
    \caption{Mesh at time $t = 10^{-3}$.}
  \end{subfigure}%
  \caption{Numerical solutions of a supersonic jet with Mach number 2000 using
           sub-cell entropy-dissipative shock-capturing methods with sub-cell positivity-preserving
           limiters and adaptive mesh refinement for the compressible Euler equations.}
  \label{fig:jet}
\end{figure}

@@

\begin{figure}[!h]
  \includegraphics[width=\linewidth]{../figures/pid_euler_mesh}
  \caption{Initial density of the compressible Euler problem on the curved mesh
           used for the performance benchmarks.}
  \label{fig:pid_euler_mesh}
\end{figure}

>>>>

Currently, \trixi provides shared-memory parallelization via multithreading.
Distributed-memory parallelization with MPI is available for some mesh types
but still work in progress.

@@

Figure~\ref{fig:jet} demonstrates sub-cell entropy-dissipative shock-capturing
methods with sub-cell positivity-preserving limiters and adaptive mesh refinement applied
to an astrophysical supersonic jet with Mach number 2000 \cite{liu2021oscillation}.
\begin{figure}[!h]
\vspace{-0.5em}
  \begin{subfigure}{0.53\linewidth}
    \includegraphics[width=\textwidth]{../figures/jet_density}
    \caption{Density at time $t = 10^{-3}$.}
  \end{subfigure}%
  \hspace*{\fill}
  \begin{subfigure}{0.47\linewidth}
    \includegraphics[width=\textwidth]{../figures/jet_mesh}
    \caption{Mesh at time $t = 10^{-3}$.}
  \end{subfigure}%
  \caption{Numerical solutions of a supersonic jet with Mach number 2000 using
           sub-cell entropy-dissipative shock-capturing methods with sub-cell positivity-preserving
           limiters and adaptive mesh refinement for the compressible Euler equations.}
  \label{fig:jet}
\end{figure}

@@

\begin{figure}[!h]
  \includegraphics[width=\linewidth]{../figures/pid_euler_mesh}
  \caption{Initial density of the compressible Euler problem on a slice of the
           periodic, curved mesh used for the performance benchmarks.}
  \label{fig:pid_euler_mesh}
\end{figure}
